%----------------------------------------------------------------------------------------
%	DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{cv}
\title{Curriculum Vitae}
\author{Christopher Buckley}
\name{Christopher Mark Buckley B.Sc. (Hons) Dunelm}
\address{Email: chris@cmbuckley.co.uk}

\hypersetup{
    pdflang=en-GB,
    pdfcreator=pdflatex,
    bookmarksopen=true
}

\begin{document}

\section{Alma Mater}

\begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries 2006--present}]
\item[2006--present] Department of Computer Science, University of Durham
\item[2003--2006] College of St Hild \& St Bede, University of Durham
\item[1996--2003] Tadcaster Grammar School, Tadcaster
\item[1990--1996] Scholes Elmet Primary School, Leeds
\end{description}

\section{Current Status}

\subsection*{Masters by Research in Computer Science}

I am working towards a postgraduate master's degree in Computer Science. This involves 12 months of study into the field of Information Theory, and specifically Network Coding. I am also in the process of writing a joint academic paper with S{\o}ren Riis and Stefan Dantchev.

\section{Qualifications}

\subsection*{Degree}

BSc Natural Sciences (Computer Science \& Mathematics)\\
Upper Second-Class Honours (2:1)

\subsection*{Computing courses undertaken}

\begin{description}[style=nextline]
\item[Computer science project] Single-handed development of a computerised adaptive testing system
\item[Software Engineering] Development techniques and techniques for re-engineering legacy systems
\item[Group project] Working in a development team to produce a stocks \& shares system
\item[Formal Aspects] Study of the formal logic behind algebraic computation
\item[Computer Systems] Study of underlying software and hardware architecture
\end{description}

\subsection*{A levels}

\begin{itemize}
\item A --- Mathematics
\item A --- Further Mathematics
\item A --- Physics
\item A --- Computing
\end{itemize}

\subsection*{AS levels}

\begin{itemize}
\item A --- English Language
\end{itemize}

\subsection*{GCSEs}

\begin{itemize}
\item A* --- Mathematics
\item A*A* --- Science (Double Award)
\item A* --- Design \& Technology: Electronic Products
\item A* --- French
\item A* --- Geography
\item A --- English Language
\item A --- English Literature
\item A --- History
\end{itemize}

\section{Core Skills}

\begin{itemize}
\item (X)HTML standards compliance
\item CSS standards compliance
\item Ajax \& other JavaScript development
\item PHP5 object-oriented \& procedural dynamic scripting
\item MySQL database-driven applications \& database management
\item Graphic \& logo design
\end{itemize}

\section{Portfolio Sample}

\begin{description}[style=nextline]
\item[ASD Services] http://asdservices.co.uk\\
ASD Services are one of the largest suppliers of appliances to trade and retail in Yorkshire. This static website required a complete re-write to make it up-to-date and standards compliant.
\item[York Student Homes] http://yorkstudenthomes.com\\
York Student Homes is a family-owned business which have been renting houses to university students in York for over 20 years.
\item[Samui Dream] http://samuidream.co.uk\\
Samui Dream is a web site to advertise Charfran, a villa in Ko Samui, Thailand.
\end{description}

\section{Professional Experience}

\begin{experience}{Developer}{2007--Present}{Vebra Solutions}{Pocklington, North Yorkshire}
I am currently a developer of a PHP5-based web application at Vebra in Pocklington, near York.
\end{experience}

\begin{experience}{Proprietor}{2007--Present}{StarSquare Designs}{Leeds, West Yorkshire}
My start-up web design company, providing freelance XHTML/CSS web development, primarily to businesses local to the Leeds area.
\end{experience}

\begin{experience}{Sales Assistant}{2003--2007}{Hayes Garden World}{Leeds, West Yorkshire}
Worked in a variety of roles, including sales advisor and in the maintenance division. Dealt with customers and handled money on a daily basis; also provided IT support and stock control.
\end{experience}

\begin{experience}{Application Services Assistant}{2001--2002}{GE Capital}{Leeds, West Yorkshire}
After completing my work experience here, I was asked to work at this multi-national corporation in their application services department. My role was to process a high volume of requests for store cards that came through from around the country, involving highly sensitive and confidential information in a secure environment. This involved very fast and accurate computational skills as well as the personal skills required to deal with a variety of different customers.
\end{experience}

\section{Educational Experience}

\begin{experience}{President \& Treasurer}{2004--2007}{Hild Bede Mountaineering Club}{University of Durham}
In this combined role I managed most of the administrative side of the club. As well as organising events I looked after club finances and equipment. I was also the club website editor.
\end{experience}

\section{Personal Interests}

\begin{itemize}
\item Biking (UK BikeTrials Competitions)
\item Swimming
\item Rock climbing
\item Snowboarding
\item Music (lead/rhythm guitarist)
\item Computing \& web development
\end{itemize}

\end{document}
